\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-17 foci/paper.tex
Add a clause for clarity

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS.

>>>>

\subsection{Spoofing the Installation Server}
\label{dnsspoof}
An additional dangerous class of vulnerabilities comes from the lack of HTTPS during the initial installation process.  We discovered that the script that performs this installation is downloaded via TCP from an IP address provided by the Pogoplug servers.  This script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is verification of the script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server and force users to download a malicious script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Because the activation occurs over TCP, an adversary who can spoof DNS replies to the user can install arbitrary software onto the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.  We were unable to observe a post-installation update from Pogoplug due to none being provided to users in the 6+ months since the Safeplug was released, but examining the update scripts on the Safeplug indicates that this update process occurs over HTTPS, so that only the initial download during device activation is vulnerable.
